Supporting Information: Statistical Inference of Transport Mechanisms and Long Time Scale Behavior from Time Series of Solute Trajectories in Nanostructured Membranes.

### 2020-05-19 Ben_Manuscripts/hdphmm/Supporting_Information.tex
Improvements to methods
moving figures to SI

>>>>

  \section{Clustered Parameters}\label{section:clustered_parmeters}

  We can begin to hypothesize mechanisms by studying the behaviors defined by the 
  state parameters. In Figure~\ref{fig:common_states_lines}, we plot representative 
  dynamics of each of the five most visited states (see Figure~\ref{M-fig:prevalence}
  of the main text). The states exhibit a range of autoregressive and trapping 
  behavior throughout the membrane pores.

  Since the radial means are weighted averages of the states used to parameterize
  each cluster, for interpretive purposes, it is important to recognize that the means
  only provide clues towards the general location of the solute. For example, the 
  radial mean of state 3 is 1.4 nm from the pore center. However, inspection of 
  Figure~\ref{fig:clustered_traj_MET} suggests that this type of behavior actually
  occurs radially throughout the pore. There are instances of state 3 less than 1 nm
  from the pore center and more than 2 nm from the pore center. In this case, the 
  radial mean only suggests that this type of behavior happens in both regions somewhat
  equally.

  Solutes exhibit a range of autoregressive behavior as shown by the representative 
  solute trajectories in Figure~\ref{fig:common_states_lines} and the scatter
  plot in Figure~\ref{fig:A_sigma_scatter}. In most cases, the eigenvalues of $A$ and
  $\Sigma$ appear nearly paired in their radial and axial dimensions, which implies 
  nearly symmetric behavior with off-diagonals both matrices near zero. The most 
  notable exception is state 3, which has a much higher radial eigenvalue of the 
  covariance matrix. Both eigenvalues of state 3's covariance are actually quite
  large. This implies relatively large fluctuations in the $z$ direction and even
  bigger fluctuations in the $r$ direction. All states have slightly lower covariance
  in the axial direction. It's likely easier for solutes to move laterally rather 
  than to move up through the alkane chains. States 3 and 4 show a strong previous-hop
  dependence (high $A$) while the rest of the states have a somewhat weaker dependence.

  Solutes stay trapped for various lengths of time. On average, state 4 has the longest 
  dwell times and state 3 has the shortest dwell times while the rest have intermediate
  dwell times. This is somewhat supported by inspection of Figure~\ref{fig:clustered_traj_MET},
  however. The expected dwell times of the clusters incorporate all 24 trajectories.

  % BJC4: Not sure if this is useful.
  % MRS: it does give a good summary. But you should make it clear how you selected these 5.
  % MRS: it's implied in one of the figures, but should be stated explicitly
%  By examining the parameters, it is now easier to describe the state behavior.
%  \begin{enumerate}[label={State \theenumi :}, leftmargin=3.5\parindent]
%     \item This state has intermediate dwell times with high past-hop dependence.
%     The radial mean and evidence from Figure~\ref{fig:clustered_traj_MET} suggests
%     %MRS: ``tail and pore region'' sounds the same as ``everywhere''.
%     that this state is common in the tail and pore region.
%     \item This state seems to occur exclusively in the tail region based on its radial
%     mean. Its fluctuations are small and there is little past hop dependence
%     \item This is likely a hopping state that strongly contribute to the solute's MSD. 
%     It is short lived and takes very large hops. This type of behavior is exhibited 
%     %MRS: ``near and far'' also sounds like everywhere 
%     near and far from the pore center as discussed earlier.
%     \item This is a trapping state with a strong dependence on its previous fluctuation.
%     Evidence from Figure~\ref{fig:clustered_traj_MET} and a radial mean of 1.8 suggest
%     that it tends to occur at intermediate distances from the pore center.
%     \item This is an intermediate-length trapping state that occurs close to the pore
%     center. It's fluctuations are tight and relatively independent of its previous 
%     fluctuation.
%  \end{enumerate}

  \begin{figure}
  \centering
  \begin{subfigure}{0.58\textwidth}
  \includegraphics[width=\textwidth]{common_states.pdf}
  \caption{}\label{fig:common_states_lines}
  \end{subfigure}
  \begin{subfigure}{0.41\textwidth}
  \includegraphics[width=\textwidth]{A_sigma_scatter.pdf}
  \caption{}\label{fig:A_sigma_scatter}
  \includegraphics[width=\textwidth]{dwell_times.pdf}
  \caption{}\label{fig:dwell_times}
  \end{subfigure}
  \caption{The 5 most visited states by methanol show a range of dynamical behavior. In 
  (a), we show representative dynamics of these states. All time series have a mean of zero and are
  shifted to put the mean in line with the $y$-axis labels for the purpose of visualizing them.
  The $y$-axis labels of the $r$ coordinate plot specify the radial mean of each clustered 
  state. All of the states pictured appear in the trajectory shown in 
  Figure~\ref{M-fig:clustered_traj_MET} of the main text and are colored to match.
  (b) We can begin to understand the solute behaviors demonstrated in (a) by understanding their VAR 
  parameters. Higher values of $\lambda_{\Sigma}$ generally are indicative of large fluctuations
  and higher values of $\lambda_A$ indicate strong previous-hop dependence of the fluctuations.
  (c) Using Equation~\ref{M-eqn:dwell_times} of the main text, we estimated the expected time spent within each 
  of the states.
  }\label{fig:common_states_MET}
  \end{figure}
